---
title: "Appendix"
author: "Statistics Final project"
date: "2023-11-27"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
mobile_dataset<-read.csv("MobilePrice.csv",header = TRUE) 
names(mobile_dataset)
```
Pie Chart
```{r}

library(ggplot2)
ggplot(mobile_dataset, aes(x = "", fill = factor(price_range))) +
  geom_bar(width = 1, stat = "count") +
  coord_polar("y") +
  labs(title = "Distribution of Price Ranges") +
  theme_void() +
  scale_fill_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3"))+
  labs(title = "Distribution of four_g Variable") +
  ylab("Price Range") +
  theme_minimal()

```
BAR CHART:
```{r}
ggplot(mobile_dataset, aes(x = factor(four_g))) +
  geom_bar(fill = c("violet", "skyblue")) +  # Set colors for 1 and 0
  labs(title = "Distribution of four_g Variable") +
  xlab("four_g") +
  ylab("Frequency") +
  theme_minimal()

```

Histogram:
```{r}
hist(mobile_dataset$battery_power,main = "Histogram of battery power",
     xlab = "battery power",col ="pink")
hist(mobile_dataset$ram,main = "Histogram of Ram power",xlab = "Ram",
     col="lightgreen")
hist(mobile_dataset$px_width,main = "Histogram of px_width",
     xlab = "px_width",col="violet")
hist(mobile_dataset$px_height,main = "Histogram of px_height",
     xlab = "px_height",col="lightblue")
```

boxplot
```{r}

library(ggplot2)
par(mfrow = c(2, 2))
ggplot(mobile_dataset,aes(x=as.factor(price_range), y=battery_power,
                          fill=as.factor(price_range))) + geom_boxplot()+ labs(
    x = "Price range",
    y = "battery_power",
    title = "Battery_power vs Price Range"
  )
ggplot(mobile_dataset,aes(x=as.factor(price_range), y=px_height, 
                          fill=as.factor(price_range))) + geom_boxplot()+ labs(
    x = "Price range",
    y = "px_height",
    title = "px_height vs Price Range"
  )
ggplot(mobile_dataset,aes(x=as.factor(price_range), y=px_width, 
                          fill=as.factor(price_range))) + geom_boxplot()+labs(
    x = "Price range",
    y = "px_width",
    title = "px_width vs Price Range"
  )
ggplot(mobile_dataset,aes(x=as.factor(price_range), y=ram, 
                          fill=as.factor(price_range))) + geom_boxplot()+labs(
    x = "Price range",
    y = "ram",
    title = "ram vs Price Range"
  )

ggplot(mobile_dataset,aes(x=as.factor(price_range), y=int_memory,
                          fill=as.factor(price_range))) + geom_boxplot()+labs(
    x = "Price range",
    y = "int_memory",
    title = "int_memory vs Price Range"
  )
ggplot(mobile_dataset,aes(x=as.factor(price_range), y=pc, 
                          fill=as.factor(price_range))) + geom_boxplot()+labs(
    x = "Price range",
    y = "pc",
    title = "int_memory vs Price Range"
  )
#We can see a huge difference in battery power between the price_range 0 and 
#the price_range 3 but not so much between the 1 and 2.
```
Hypothesis testing
one-sample hypothesis test:
#Average battery power 
```{r}
battery_power_mean <- 1238 # average battery_power
t.test(mobile_dataset$battery_power,mu=1238,alternative = "less",
       conf.level = 0.95)
#Do not reject as p value is greater than 0.05
#It means that we dont have enough evidence that the average battery power 
#is less than 1238
```
Two sample hypothesis test:
Null Hypothesis (H0): There is no difference in the average battery power 
between phones with and without 4G.
Alternative Hypothesis (H1): There is a significant difference in the average 
battery power between phones with and without 4G.
```{r}
battery_power_4g <- mobile_dataset$battery_power[mobile_dataset$four_g == 1]
battery_power_no_4g <- mobile_dataset$battery_power[mobile_dataset$four_g == 0]
t_test_result <- t.test(battery_power_4g, battery_power_no_4g)
t_test_result
#Reject the hypothesis as there is a significant difference in average battery
# power between phones with and without 4G.
```

Null Hypothesis (H0): There is no difference in the average RAM between phones
with and without dual SIM.
Alternative Hypothesis (H1): There is a significant difference in the average 
RAM between phones with and without dual SIM.
```{r}
ram_dual_sim <- mobile_dataset$ram[mobile_dataset$dual_sim == 1]
ram_no_dual_sim <- mobile_dataset$ram[mobile_dataset$dual_sim == 0]
t_test_result <- t.test(ram_dual_sim, ram_no_dual_sim)
print(t_test_result)
#reject the hypothesis as there is a significant difference in average ram
# between phones with and without dual sim.
```

ANOVA:
```{r}
anova_result <- aov(battery_power ~ price_range, data = mobile_dataset)
summary(anova_result)

anova_result1 <- aov(px_height ~ price_range, data = mobile_dataset)
summary(anova_result1)

anova_result2 <- aov(ram ~ price_range, data = mobile_dataset)
summary(anova_result2)

anova_result3 <- aov(px_width ~ price_range, data = mobile_dataset)
summary(anova_result3)

anova_result4 <- aov(int_memory ~ price_range, data = mobile_dataset)
summary(anova_result4)

anova_result5 <- aov(pc ~ price_range, data = mobile_dataset)
summary(anova_result5)
```
CHI-SQUARE:
```{r}
chi_squared_result_3g <- chisq.test(table(mobile_dataset$three_g,
                                          mobile_dataset$price_range))
chi_squared_result_3g

chi_squared_result_sim <- chisq.test(table(mobile_dataset$four_g, 
                                           mobile_dataset$price_range))
chi_squared_result_sim
#If the p-value is less than the significance level (0.05), we reject the null 
#hypothesis, suggesting evidence of an association.
```
shapiro test

```{r}
shapiro_test_result <- shapiro.test(mobile_dataset$ram)
shapiro_test_result
#The data is not normally distributed.
```

# Levene's test for homogeneity of variances
```{r}
if (!requireNamespace("car", quietly = TRUE)) {
  install.packages("car")
}
library(car)
levene_test_result <- leveneTest(mobile_dataset$battery_power, 
                                 group = mobile_dataset$price_range)
levene_test_result
#Variances are significantly different across groups.
```
Kruskal-Wallis test(alternative to Anova test)
```{r}
#install.packages("coin")
library(coin)

kw_result1 <- kruskal.test(battery_power ~ price_range, data = mobile_dataset)
kw_result2 <- kruskal.test(px_height ~ price_range, data = mobile_dataset)
kw_result3 <- kruskal.test(ram ~ price_range, data = mobile_dataset)
kw_result4 <- kruskal.test(px_width ~ price_range, data = mobile_dataset)
kw_result5 <- kruskal.test(int_memory ~ price_range, data = mobile_dataset)
kw_result6 <- kruskal.test(pc ~ price_range, data = mobile_dataset)

print(kw_result1)
print(kw_result2)
print(kw_result3)
print(kw_result4)
print(kw_result5)
print(kw_result6)

```

